Manual of comparing optimal subsampling with model robust optimal subsampling method for poisson regression (standardised Multivariate Normal distribution)

### 2022-06-27 Manual.Rmd
updated manual and readme file with diagrams and brief summary

---
title: "Manual of comparing optimal subsampling with model robust optimal subsampling method for poisson regression (standardised Multivariate Normal distribution)"
output: github_document
---

>>>>

---
title: "Manual of comparing optimal subsampling with model robust optimal subsampling method for poisson regression (standardised Multivariate Normal distribution)"
output: 
  html_document:
    keep_md: yes
---
